---
title: "QRP prevalence perception from multiple papers"
author: "Jason Chin & Alex O. Holcombe"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup}
#loads libraries for working with data
library(tidyverse)
library(readr)
knitr::opts_chunk$set(echo = TRUE, 
 echo=TRUE, eval=TRUE, warning=T, message=T)

#https://datavizpyr.com/rain-cloud-plots-using-half-violin-plot-with-jittered-data-points-in-r/
#Load half violin plot: geom_flat_violin()
source("https://raw.githubusercontent.com/datavizpyr/data/master/half_flat_violinplot.R")
```

```{r}
brazilPath<-file.path("RabeloEtAl","Data")
brazil<- readRDS(file.path(brazilPath,"prevalenceLongAfterAlexEditingAndRunningBrazilCode.rds"))
table(brazil$QRP,brazil$QRP_type)
brazilPr <- brazil %>% filter(QRP_type == "Prevalence estimate")
```

Plot Brazilian data
```{r}
QRPprevCloudBrazil <- ggplot( drop_na(brazilPr),
                                aes(x = QRP, y = val) ) + 
  theme_bw() +
  geom_flat_violin(fill="gray32",color="gray32", position = position_nudge(x = .18, y = 0)) +
  geom_jitter(alpha=0.1, size=.5, width=0.15, height=0) +
  stat_summary(fun = mean, geom = "point", color='green4', size=4, alpha=0.82) +
  stat_summary(fun.data = mean_cl_boot, fun.args=(conf.int=0.95), geom="errorbar", size=.9, width=0.1, color='green4', alpha=0.82) +
  #geom_jitter(width=0.2, size=.2, alpha=0.1)+
  xlab("QRP") + ylab("perceived % others use at least once") + ylim(0,100) +
  labs(title='Perceived prevalence of QRPs used by a researcher on at least one occasion') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 12)) 
show(QRPprevCloudBrazil)
```

Rename practices to standard names in Brazilian dataset.

Probably should plot Brazil, Agnoli, and John on one plot, others on another.

```{r }
#Give practice same name as for other studies
brazil<- brazil %>% mutate(
  practiceStandardName = case_when(
    QRP=="Omitting measures" ~ "Not report all DVs\n(closest to Omit n.s. studies or variables)",
    QRP=="Collecting data based on results" ~ "Sample selectively",
    QRP=="Omitting conditions" ~ "Not report all conditions\n(closest to Omit n.s. studies or variables)",
    QRP=="Stopping data collection" ~ "Stop collecting data bc sig\n(closest to Sample selectively)",
    QRP=="Rounding off p-values" ~ "Round p-values",
    QRP=="Reporting studies that worked" ~ "Reporting only studies that worked", #In a paper, selectively reporting studies that “worked”
    QRP=="Excluding data based on results" ~ "Exclude data selectively",
    QRP=="A posteriori hypothesizing" ~ "HARK",
    QRP=="Demographics" ~ "Mislead about demographic\nvariable effects",
    QRP=="Falsifying data" ~ "Falsify data\n(closest to Hide imputation)",
    TRUE    ~ "ERROR! unknown practice"
  )
)
brazil$practiceStandardName <- as.factor(brazil$practiceStandardName)

brazilPr <- brazil %>% filter(QRP_type == "Prevalence estimate")
```

```{r}
QRPprevCloudBrazil <- ggplot( drop_na(brazilPr),
                                aes(x = practiceStandardName, y = val) ) + 
  theme_bw() +
  geom_flat_violin(fill="gray32",color="gray32", position = position_nudge(x = .18, y = 0)) +
  geom_jitter(alpha=0.1, size=.5, width=0.15, height=0) +
  stat_summary(fun = mean, geom = "point", color='green4', size=4, alpha=0.82) +
  stat_summary(fun.data = mean_cl_boot, fun.args=(conf.int=0.95), geom="errorbar", size=.9, width=0.1, color='green4', alpha=0.82) +
  #geom_jitter(width=0.2, size=.2, alpha=0.1)+
  xlab("QRP") + ylab("perceived % others use at least once") + ylim(0,100) +
  labs(title='Perceived prevalence of QRPs used by a researcher on at least one occasion') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 12)) 
show(QRPprevCloudBrazil)
```

Load and bind together differnt studies' data

```{r }
Chin <- readRDS( "longQRPs.rds" )
Chin <- Chin %>% rename( practiceStandardName = practiceLongName )
Chin <- Chin %>% rename( value = response )

Makel <- readRDS( file.path("Makel_Agnoli","Makel_longQRPs.rds") )

Agnoli <- readRDS( file.path("Makel_Agnoli","Agnoli_LongQRPs.rds") )

Chin$field <- "criminology"
Makel$field<- "education"
Agnoli$field<-"psychology"

Chin$study <- "Chin (criminology)"
Makel$study <- "Makel (education)"
Agnoli$study <- "Agnoli (psychology)"

Fraser <- readRDS( file.path("FraserEtAl","longQRPs.rds") )
Fraser<- Fraser %>% mutate(
    study = case_when(
      field=="ecology" ~ "Fraser (ecology)",
      field=="evolutionary biology" ~ "Fraser (evolutionary biology)",
      TRUE ~ "ERROR! unknown field"
  ))
  
Fraser <- Fraser %>% mutate( practiceStandardName = practice )

CMAF <- rbind(Chin,Makel)
CMAF <- rbind(CMAF,Agnoli)
CMAF <- rbind(CMAF,Fraser)

```

Reorder levels for more pleasing and logical ordering, of both practices and studies

```{r }
#levels(CMAF$practiceStandardName)
practiceOrderDesiredNeverAscending <- c(1,14,2,3,4,11,5,6,7,12,8,9,10,16,13,15) #order from least endorsed to most endorsed
CMAF$practiceStandardName <- factor(CMAF$practiceStandardName,
                                    levels = levels(CMAF$practiceStandardName)[practiceOrderDesiredNeverAscending])

CMAF$study <- as.factor(CMAF$study)
levels(CMAF$study)
studyOrderDesired <- c(1,5,2,3,4) #order from least endorsed to most endorsed
CMAF$study <- factor(CMAF$study,
                     levels = levels(CMAF$study)[studyOrderDesired])

```

Plot including all fields, even ones that were only in Agnoli.
```{r }
#Better to compare the distributions horizontally for the same study, but facet labels are too long to fit.
# QRPprevCloud <- ggplot( drop_na(CMAF),
#                         aes(x = study, y = value) ) + 
#   theme_bw() + facet_grid(practiceStandardName ~.) +
#   geom_flat_violin(fill="gray32",color="gray32", position = position_nudge(x = .18, y = 0)) +
#   geom_jitter(alpha=0.1, size=.5, width=0.15, height=0) +
#   stat_summary(fun = mean, geom = "point", color='green4', size=4, alpha=0.82) +
#   stat_summary(fun.data = mean_cl_boot, fun.args=(conf.int=0.95), geom="errorbar", size=.9, width=0.1, color='green4', alpha=0.82) +
#   #geom_jitter(width=0.2, size=.2, alpha=0.1)+
#   xlab("QRP") + ylab("perceived % others use at least once") + ylim(0,100) +
#   labs(title='Perceived prevalence of QRPs used by a researcher on at least one occasion') +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 12)) 
# show(QRPprevCloud)

QRPprevCloudComplete <- ggplot( drop_na(CMAF),
                        aes(x = practiceStandardName, y = value) ) + 
  theme_bw() + facet_grid(study~.) +
  geom_flat_violin(fill="gray32",color="gray32", position = position_nudge(x = .18, y = 0)) +
  geom_jitter(alpha=0.1, size=.5, width=0.15, height=0) +
  stat_summary(fun = mean, geom = "point", color='green4', size=4, alpha=0.82) +
  stat_summary(fun.data = mean_cl_boot, fun.args=(conf.int=0.95), geom="errorbar", size=.9, width=0.1, color='green4', alpha=0.82) +
  #geom_jitter(width=0.2, size=.2, alpha=0.1)+
  xlab("QRP") + ylab("perceived % others use at least once") + ylim(0,100) +
  labs(title='Perceived prevalence of QRPs used by a researcher on at least one occasion') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 12)) 
show(QRPprevCloudComplete)
ggsave( file.path("figures","MultipleStudiesPrevalencePerceptionDistributionsComplete.png"), width = 50, height = 30, units = "cm" )
```

Plot but don't include ones only in Agnoli, Brazil, and John et al.

```{r }
#Falsify data - John et al. had that, Agnoli et al, and Rabelo et al. 
  
omitExtraAgnoli <- CMAF %>% filter(practiceStandardName != "Mislead about demographic\nvariable effects") %>%
      filter(practiceStandardName != "Not report all conditions\n(closest to Omit n.s. studies or variables)") %>%
      filter(practiceStandardName != "Falsify data\n(closest to Hide imputation)") %>%
      filter(practiceStandardName != "Not report all DVs\n(closest to Omit n.s. studies or variables)") %>%
      filter(practiceStandardName != "Stop collecting data bc sig\n(closest to Sample selectively)"  )

QRPprevCloudLess <- ggplot( drop_na(omitExtraAgnoli),
                        aes(x = practiceStandardName, y = value) ) + 
  theme_bw() + facet_grid(study~.) +
  geom_flat_violin(fill="gray32",color="gray32", position = position_nudge(x = .18, y = 0)) +
  geom_jitter(alpha=0.1, size=.5, width=0.15, height=0) +
  stat_summary(fun = mean, geom = "point", color='green4', size=4, alpha=0.82) +
  stat_summary(fun.data = mean_cl_boot, fun.args=(conf.int=0.95), geom="errorbar", size=.9, width=0.1, color='green4', alpha=0.82) +
  #geom_jitter(width=0.2, size=.2, alpha=0.1)+
  xlab("QRP") + ylab("perceived % others use at least once") + ylim(0,100) +
  labs(title='Perceived prevalence of QRPs used by a researcher on at least one occasion') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 12)) 
show(QRPprevCloudLess)
ggsave( file.path("figures","MultipleStudiesPrevalencePerceptionDistributionsLess.png"), width = 50, height = 30, units = "cm" )
```



